\cvsection{Experience}
\begin{cventries}
  \cventry%
    {Graduate Research Assistant, PI:\ Prof.~J.~Christian Gerdes}
    {Dynamic Design Lab}
    {Stanford, CA}
    {Sep.\ 2009--PRESENT}
    {
      \begin{cvitems}
        \item{Collected, compiled, analyzed, and openly published vehicle dynamics data from highly-skilled professional race car drivers during live racing events to gain insights into vehicle control at the limits of handling.}
        \item{Compared human performance with autonomous vehicles to improve operating capabilities of active vehicle safety systems.}
        \item{Implemented autonomous vehicle control using drive-by-wire hardware and convex optimization software to operate at the handling limits while following a desired trajectory.}
        \item{Implemented and tested control algorithms on experimental vehicles using C and MATLAB\@.}
        \item{Pioneered a comprehensive, noninvasive vehicle instrumentation suite for vintage race cars with significant historical value.}
        \item{Developed a graphical user interface in MATLAB for vehicle data visualization and exploratory data analysis.}
        \item{Assembled and maintained an end-to-end solution from surveyed GNSS base stations to on-board integrated navigation systems enabling research vehicles to operate reliably with centimeter-level position measurement accuracy.}
        \item{Installed and operated a Linux-based NTRIP caster to broadcast Differential GNSS corrections from multiple servers to multiple clients.}
      \end{cvitems}
    }

  \cventry%
    {Senior Teaching Assistant --- Mechanical Systems Design, Profs.~Mark Cutkosky and~Paul Mitiguy}
    {Stanford Department of Mechanical Engineering}
    {Stanford, CA}
    {Jan.--Mar.\ 2016}
    {
      \begin{cvitems}
        \item{Developed curriculum and coordinated team of five other teaching assistants.}
        \item{Led hands-on laboratory and tutorial sessions for course with 150 undergraduates exploring characteristics of machine elements.}
        \item{Advised design-project teams emphasizing the balance of physical and virtual prototyping based on engineering analysis.}
      \end{cvitems}
    }

  \cventry%
    {Teaching Assistant --- Mechanical Systems Design, Prof.~J. Christian Gerdes}
    {}
    {}
    {Jan.--Mar.\ 2012}
    {
      \begin{cvitems}
        \item{Aided hands-on laboratory and tutorial sessions for course with 150 undergraduates exploring characteristics of machine elements.}
        \item{Advised design-project teams emphasizing the balance of physical and virtual prototyping based on engineering analysis.}
      \end{cvitems}
    }

  \cventry%
    {Teaching Assistant --- Mechanical Engineering Freshman Laboratory, Prof.~Allison Okamura}
    {Johns Hopkins Department of Mechanical Engineering}
    {Baltimore, MD}
    {Sep.--Dec.\ 2008}
    {
      \begin{cvitems}
        \item{Helped plan, organize, and conduct weekly hands-on laboratory sessions.}
        \item{Provided assistance during weekly laboratory sessions for approximately 20 students per session exploring basic physical science and engineering principles pertaining to mechanical engineering.}
      \end{cvitems}
    }

 \cventry%
   {Undergraduate Research Assistant, PI:\ Profs.~Charles Meneveau and~Joseph Katz}
   {}
   {}
   {Jan.--May 2007}
   {
     \begin{cvitems}
       \item{Designed and documented new test section, including a fractal canopy, for the project titled \textit{Measuring and Modeling Interactions of the Turbulent Atmospheric Boundary Layer with Multiscale Ground Topology} to be conducted in the laboratory's axial turbomachinery water tunnel.}
     \end{cvitems}
   }

  \cventry%
    {Biomedicine Group Intern, PI:\ Dr.~James Beaty}
    {Johns Hopkins University Applied Physics Laboratory}
    {Laurel, MD}
    {May--Aug.\ 2008}
    {
      \begin{cvitems}
        \item{Developed method for capturing primate hand motion using Vicon cameras for the Revolutionizing Prosthetics Program.}
        \item{Designed and installed two on-site camera systems, prepared internal manual documentation, and trained multiple staff members to use the system proficiently.}
      \end{cvitems}
    }

 \cventry%
   {Langley Aerospace Research Summer Scholar, PI:\ Steven Bauer}
   {NASA Langley Research Center}
   {Hampton, VA}
   {Jun.--Aug.\ 2007}
   {
     \begin{cvitems}
       \item{Collected and compiled experimental data from wind tunnel testing of the separation event of Ares I-X, the experimental flight test vehicle for NASA's next crew launch vehicle.}
       \item{Collected, compiled, and analyzed computational data using NASA-developed computational fluid dynamics (CFD) software for the descent database of the Upper Stage Simulator.}
     \end{cvitems}
   }

 \cventry%
   {Chief Investigator, PI:\ Dick Deloach}
   {New Horizons Governor's School for Science and Technology}
   {Hampton, VA}
   {Sep.\ 2004--May 2005}
   {
     \begin{cvitems}
       \item{Research and mentorship porgram with NASA Langley Research Center.}
       \item{Investigated various swimming techniques by applying the Modern Design of Experiments to the biomechanics of swimming.}
     \end{cvitems}
   }
\end{cventries}
